### 2020-08-11 code/figure4.Rmd
fixes error in plotting of heatmap in figure4 that used to incorrectly compute the number of mutations independent of cluster.

tdat_up <- all_muts %>%
  filter(Hugo_Symbol %in% up_compare_plot$Hugo_Symbol) %>%
  distinct(Tumor_Sample_Barcode, Hugo_Symbol, clust_knn_char, type) %>%
  select(type, Hugo_Symbol) %>%
  table()

tdat_up <- left_join(as.data.frame(tdat_up), 
                  clinical_plus_cluster %>%
                    select(Tumor_Sample_Barcode, type, clust_knn_char) %>% 
                    distinct() %>% 
                    group_by(type, clust_knn_char) %>% 
                    summarise(ntumors = n())) %>% 
  mutate(prop = Freq / ntumors) %>%
  select(type, Hugo_Symbol, prop) %>%
  left_join(up_compare_plot %>% select(Hugo_Symbol, cluster))
tdat_up$Hugo_Symbol <- factor(tdat_up$Hugo_Symbol, levels = levels(up_compare_plot$Hugo_Symbol))

@@

tdat_dn <- all_muts %>%
  filter(Hugo_Symbol %in% down_compare_plot$Hugo_Symbol) %>%
  distinct(Tumor_Sample_Barcode, Hugo_Symbol, clust_knn_char, type) %>%
  select(type, Hugo_Symbol) %>%
  table()
tdat_dn <- left_join(as.data.frame(tdat_dn), 
                     clinical_plus_cluster %>%
                       select(Tumor_Sample_Barcode, type, clust_knn_char) %>% 
                       distinct() %>% 
                       group_by(type, clust_knn_char) %>% 
                       summarise(ntumors = n())) %>% 
  mutate(prop = Freq / ntumors) %>%
  select(type, Hugo_Symbol, prop) %>%
  left_join(down_compare_plot %>% select(Hugo_Symbol, cluster))
tdat_dn$Hugo_Symbol <- factor(tdat_dn$Hugo_Symbol, levels = levels(down_compare_plot$Hugo_Symbol))

>>>>

tdat_up <- all_muts %>%
  filter(Hugo_Symbol %in% up_compare_plot$Hugo_Symbol) %>%
  distinct(Tumor_Sample_Barcode, Hugo_Symbol, clust_knn_char, type) %>%
  select(type, clust_knn_char, Hugo_Symbol) %>%
  table()

tdat_up <- left_join(as.data.frame(tdat_up), 
                  clinical_plus_cluster %>%
                    select(Tumor_Sample_Barcode, type, clust_knn_char) %>% 
                    distinct() %>% 
                    group_by(type, clust_knn_char) %>% 
                    summarise(ntumors = n())) %>% 
  mutate(prop = Freq / ntumors) %>%
  mutate(prop = ifelse(is.na(prop), 0, prop)) %>%
  select(type, Hugo_Symbol, prop) %>%
  left_join(up_compare_plot %>% select(Hugo_Symbol, cluster))
tdat_up$Hugo_Symbol <- factor(tdat_up$Hugo_Symbol, levels = levels(up_compare_plot$Hugo_Symbol))

@@

tdat_dn <- all_muts %>%
  filter(Hugo_Symbol %in% down_compare_plot$Hugo_Symbol) %>%
  distinct(Tumor_Sample_Barcode, Hugo_Symbol, clust_knn_char, type) %>%
  select(type, clust_knn_char, Hugo_Symbol) %>%
  table()
tdat_dn <- left_join(as.data.frame(tdat_dn), 
                     clinical_plus_cluster %>%
                       select(Tumor_Sample_Barcode, type, clust_knn_char) %>% 
                       distinct() %>% 
                       group_by(type, clust_knn_char) %>% 
                       summarise(ntumors = n())) %>% 
  mutate(prop = Freq / ntumors) %>%
  mutate(prop = ifelse(is.na(prop), 0, prop)) %>%
  select(type, Hugo_Symbol, prop) %>%
  left_join(down_compare_plot %>% select(Hugo_Symbol, cluster))
tdat_dn$Hugo_Symbol <- factor(tdat_dn$Hugo_Symbol, levels = levels(down_compare_plot$Hugo_Symbol))
